### 2022-04-26 paper/localpsf.tex
update changes during discussion with Tucker

If $\Aop$ is symmetric positive definite, we symmetrize $\mathbf{A}_H$ as follows
\begin{equation*}
\mathbf{A}_H^{\text{sym}} := \frac{1}{2}\left(\mathbf{A}_H + \mathbf{A}_H^T\right).
\end{equation*}
Then we compute the negative eigenvalues, of $\mathbf{A}_H$ that are less than (i.e., more negative than) a small magnitude negative cutoff value $c$, and also compute the corresponding eigenvectors. That is, the eigenpairs $\{(\lambda_i,u_i)\}_{i=1}^{N_\text{bad}}$ with
\begin{equation*}
	\lambda_i < c < 0.
\end{equation*}
These outlying ``bad'' eigenpairs are computed using the Lanczos method \cite{Komzsik03,Lanczos50}.
We then flip the sign of these negative eigenvalues to be positive as follows:
\begin{equation*}
	\mathbf{A}_H^{\text{sym}+} = \mathbf{A}_H^{\text{sym}} + \sum_{i=1}^{N_\text{bad}} 2 |\lambda_i| u_i u_i^T.
\end{equation*}
The matrix $\mathbf{A}_H^{\text{sym}+}$ approximates the matrix absolute value of $\mathbf{A}_H^{\text{sym}}$. A H-matrix representation of $\mathbf{A}_H^{\text{sym}+}$ is formed using H-matrix addition, and used in place of $\mathbf{A}_H$ in further linear algebra operations.

>>>>

If $\Aop$ is symmetric positive definite, we symmetrize $\mathbf{A}_H$ as follows
\begin{equation*}
\mathbf{A}_H^{\text{sym}} := \frac{1}{2}\left(\mathbf{A}_H + \mathbf{A}_H^T\right).
\end{equation*}
Then we use the high order rational function spectral projection method from \cite{HackbuschKress07} to replace the negative eigenvalues of $\mathbf{A}_H^{\text{sym}}$ with zero (or approximately zero) while keeping the positive eigenvalues unchanged (approximately unchanged).

Then we compute the negative eigenvalues, of $\mathbf{A}_H$ that are less than (i.e., more negative than) a small magnitude negative cutoff value $c$, and also compute the corresponding eigenvectors. That is, the eigenpairs $\{(\lambda_i,u_i)\}_{i=1}^{N_\text{bad}}$ with
\begin{equation*}
	\lambda_i < c < 0.
\end{equation*}
These outlying ``bad'' eigenpairs are computed using the Lanczos method \cite{Komzsik03,Lanczos50}.
We then flip the sign of these negative eigenvalues to be positive as follows:
\begin{equation*}
	\mathbf{A}_H^{\text{sym}+} = \mathbf{A}_H^{\text{sym}} + \sum_{i=1}^{N_\text{bad}} 2 |\lambda_i| u_i u_i^T.
\end{equation*}
The matrix $\mathbf{A}_H^{\text{sym}+}$ approximates the matrix absolute value of $\mathbf{A}_H^{\text{sym}}$. A H-matrix representation of $\mathbf{A}_H^{\text{sym}+}$ is formed using H-matrix addition, and used in place of $\mathbf{A}_H$ in further linear algebra operations.
